Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2024-12-05 presentation/theory.tex
slide edits

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Theory}
  \textbf{Hybrid $\bm{S_N}$-Diffusion Method}
  \begin{block}{\textbf{Aim}}
    To enable accurate control rod modeling in time-dependent molten salt reactor simulations
  \end{block}
  \begin{block}{\textbf{Method Overview}}
    \begin{itemize}
      \item Applies the discrete ordinates ($S_N$) method to a small subregion around a
        control rod to generate corrections for the neutron diffusion equation
      \item Limits computationally expensive $S_N$ calculations to small subdomains
      \item Retains the computational efficiency of the neutron diffusion method
    \end{itemize}
  \end{block}
\end{frame}

@@

  \begin{block}{\textbf{Implementation Details}}
    \begin{itemize}
      \item Expressed in weak form for the continuous finite element method (CFEM)
      \item Compatible with the efficient and scalable Hypre-BoomerAMG preconditioning
      \item Modified formulation to handle $1/\Sigma_{t,g}$ factor in void regions (similar to
        Streamline-Upwind/Petrov Galerkin (SUPG) stabilization scheme) \cite{wang_diffusion_2014}
      \item Level-symmetric quadrature set for angular discretization (up to $S_{18}$)
      \item Nonlinear diffusion acceleration scheme \cite{wang_diffusion_2014}
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Theory}
  \textbf{Weak Formulation of the Multigroup SAAF $S_N$ Equations}
  \begin{gather}
    \shortintertext{Void stabilization parameter \cite{wang_diffusion_2014}:}
    \tau_g =
    \begin{cases}
      \frac{1}{c\Sigma_{t,g}} \mbox{ for } ch\Sigma_{t,g} \geq \varsigma \\
      \frac{h}{\varsigma} \mbox{ for } ch\Sigma_{t,g} < \varsigma
    \end{cases}, \\
    \shortintertext{where}
    \begin{align*}
      h &= \mbox{mesh element size,} & \\
      c &= \mbox{maximum stabilization factor,} & \\
      \varsigma &= \mbox{void constant.} &
    \end{align*}
  \end{gather}
  $c=1$ and $\varsigma=0.5$ by default
\end{frame}

@@

  In this work, I investigated two transport correction schemes. The first scheme is the diffusion
  correction scheme inspired by Fick's first law of diffusion:
  \begin{gather}
    D^s_g(x) = -J^{tr}_g(x)\bigg/\frac{d\phi^{tr}_g(x)}{dx} \label{eq:svdc}
  \end{gather}
  %
  where $D^s_g$ is the diffusion correction parameter, and the $tr$ superscript denotes the
  transport-derived neutron current and scalar flux solutions from the $S_N$ method.
  \vspace{.2cm}

  $D^s_g$ provides pointwise corrections to closely match the diffusion flux solution to the $S_N$
  flux solution.
  By replacing $D_g$ with $D^s_g$, we are effectively adding the following transport correction term
  %
  \begin{gather}
    -\frac{\partial}{\partial x}(D^s_g-D_g)\frac{\partial\phi_g}{\partial x}
  \end{gather}
  to the neutron diffusion equations.
\end{frame}

@@

  The second scheme is the drift correction scheme arising from adding a drift term to the neutron
  diffusion equations:
  \begin{gather}
  \scalebox{0.95}{$
    \vec{D}_g = \frac{\sum^{N_d}_{d=1}w_d\left(\tau_g\hat{\Omega}_d\hat{\Omega}_d\cdot\nabla\Psi_{g,d}
    + \left(\tau_g\Sigma_{t,g}-1\right)\hat{\Omega}_d\Psi_{g,d}
    - \tau_g\sum^G_{g'=1}\Sigma^{g'\rightarrow g}_{s,1}\hat{\Omega}_d\Psi_{g',d}
- D_g\nabla\Psi_{g,d}\right)}{\sum^{N_d}_{d=1}w_d\Psi_{g,d}},$} \label{eq:drift} \\
  \scalebox{0.95}{$
    \gamma_g =
    \frac{\sum_{\hat{\Omega}_d\cdot\hat{n}_b > 0}w_d |\hat{\Omega}_d\cdot\hat{n}_b |
  \Psi_{g,d}}{\sum^{N_d}_{d=1}w_d\Psi_{g,d}}.$} \label{eq:bound-coef}
  \end{gather}
  \vspace{.2cm}

  The drift term also provides pointwise corrections to the neutron diffusion equations. This
  formulation is derived from the SAAF-$S_N$ equations by integrating over the angular domain.
\end{frame}

@@

  $\vec{D}^{(i)}_g$: drift correction parameter in the $i$-th iteration
\vspace{4cm}}
  \column{.65\textwidth}
  \begin{figure}
    \centering
    \includegraphics[width=.45\textwidth]{images/algorithm}
    \begin{minipage}[b]{.49\textwidth}
      \caption{Algorithm flowchart for the hybrid $S_N$-diffusion method.}
    \end{minipage}
  \end{figure}
\end{columns}
\end{frame}

  For the hybrid $S_N$-diffusion method to converge, it requires appropriate boundary conditions for
  the $S_N$ subproblem.
  We may obtain
  the best estimate by applying the $P_1$ approximation for evaluating the neutron angular flux along
  the discrete ordinates $\hat{\Omega}_d$ of the $S_N$ angular quadrature set as follows:
  \begin{align}
    \Psi_{g,d} &\approx \frac{1}{4\pi}\left(\phi^\text{diff}_g+3\hat{\Omega}_d\cdot
    \vec{J}^\text{diff}_g\right) \nonumber \\
    &=\frac{1}{4\pi}\left(\phi^\text{diff}_g-3\hat{\Omega}_d\cdot D_g\nabla\phi^\text{diff}_g\right)
  \end{align}
  Therefore, the boundary source term for the $S_N$ subsolver is:
  \begin{gather}
    \Psi^\text{inc}_{g,d} = \frac{1}{w}
    \left(\phi^\text{diff}_g-3\hat{\Omega}_d\cdot D_g\nabla\phi^\text{diff}_g\right)
  \end{gather}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Theory}
  \textbf{Hybrid $\bm{S_N}$-Diffusion Method}
%  \begin{block}{\textbf{Aim}}
%    To enable accurate control rod modeling in time-dependent molten salt reactor simulations
%  \end{block}
  \begin{block}{\textbf{Method Overview}}
    \begin{itemize}
      \item Applies the discrete ordinates ($S_N$) method to a small subregion around a
        control rod to generate corrections for the neutron diffusion equation
      \item Limits computationally expensive $S_N$ calculations to small subdomains
      \item Retains the computational efficiency of the neutron diffusion method
      \item Applies an adaptive algorithm to smooth flux gradients near the $S_N$-diffusion interface
    \end{itemize}
  \end{block}
  \begin{figure}
    \centering
    \includegraphics[width=.7\textwidth]{hybrid-illustration}
    \caption{Illustration of the problem domains of the $S_N$ and neutron diffusion methods in an
    example 1-D problem.}
  \end{figure}
\end{frame}

@@

  \begin{block}{\textbf{Implementation Details}}
    \begin{itemize}
      \item Implemented with finite element method (FEM)
      \item Compatible with the efficient and scalable Hypre-BoomerAMG preconditioning
      \item Uses a modified formulation to handle $1/\Sigma_{t,g}$ factor in void regions (similar to
        Streamline-Upwind/Petrov Galerkin (SUPG) stabilization scheme) \cite{wang_diffusion_2014}
      \item Level-symmetric quadrature set for angular discretization (up to $S_{18}$)
      \item Nonlinear diffusion acceleration scheme \cite{wang_diffusion_2014}
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Theory}
  \textbf{Weak Formulation of the Multigroup SAAF $S_N$ Equations}
  \begin{gather}
    \shortintertext{Void stabilization parameter \cite{wang_diffusion_2014}:}
    \tau_g =
    \begin{cases}
      \frac{1}{c\Sigma_{t,g}} \mbox{ for } ch\Sigma_{t,g} \geq \varsigma \\
      \frac{h}{\varsigma} \mbox{ for } ch\Sigma_{t,g} < \varsigma
    \end{cases}, \\
    \shortintertext{where}
    \begin{align*}
      h &= \mbox{mesh element size,} & \\
      c &= \mbox{maximum stabilization factor,} & \\
      \varsigma &= \mbox{void constant.} &
    \end{align*}
  \end{gather}
  $c=1$ and $\varsigma=0.5$ by default.
  \vspace{.2cm}

  The SAAF-$S_N$ equations require this stabilization scheme
  in near-void regions where $\Sigma_{t,g}$ is very small.
\end{frame}

@@

  In this work, I investigated two transport correction schemes. The first scheme is the diffusion
  correction scheme similar to Fick's first law of diffusion:
  \begin{gather}
    D^s_g(x) = -J^{tr}_g(x)\bigg/\frac{d\phi^{tr}_g(x)}{dx} \label{eq:svdc}
  \end{gather}
  %
  where $D^s_g$ is the diffusion correction parameter, and the $tr$ superscript denotes the
  transport-derived neutron current and scalar flux solutions from the $S_N$ method.
  \vspace{.2cm}

%  $D^s_g$ provides pointwise corrections to closely match the diffusion flux solution to the $S_N$
%  flux solution.
  By replacing $D_g$ with $D^s_g$, we are effectively adding the following transport correction term
  %
  \begin{gather}
    -\nabla\cdot (D^s_g-D_g)\nabla\phi_g
  \end{gather}
  to the neutron diffusion equations.
  \vspace{.2cm}

  $\Rightarrow$ Abandoned after 1-D investigations due to division-by-zero issues near flux maximas
  and minimas.
\end{frame}

@@

  The second scheme is the drift correction scheme arising from adding a drift term
  ($\vec{D}_g\cdot\nabla \phi_g$) to the neutron diffusion equations:
  \begin{gather}
  \scalebox{0.95}{$
    \vec{D}_g = \frac{\sum^{N_d}_{d=1}w_d\left(\tau_g\hat{\Omega}_d\hat{\Omega}_d\cdot\nabla\Psi_{g,d}
    + \left(\tau_g\Sigma_{t,g}-1\right)\hat{\Omega}_d\Psi_{g,d}
    - \tau_g\sum^G_{g'=1}\Sigma^{g'\rightarrow g}_{s,1}\hat{\Omega}_d\Psi_{g',d}
- D_g\nabla\Psi_{g,d}\right)}{\sum^{N_d}_{d=1}w_d\Psi_{g,d}},$} \label{eq:drift} \\
  \scalebox{0.95}{$
    \gamma_g =
    \frac{\sum_{\hat{\Omega}_d\cdot\hat{n}_b > 0}w_d |\hat{\Omega}_d\cdot\hat{n}_b |
  \Psi_{g,d}}{\sum^{N_d}_{d=1}w_d\Psi_{g,d}}.$} \label{eq:bound-coef}
  \end{gather}
  \vspace{.2cm}

  The drift term also provides pointwise corrections to the neutron diffusion equations. This
  formulation is derived from the SAAF-$S_N$ equations by integrating over the angular domain and
  eliminating terms shared by the neutron diffusion equations.
\end{frame}

  For the hybrid $S_N$-diffusion method to converge, it requires appropriate boundary conditions for
  the $S_N$ subproblem.
  We may obtain
  the best estimate by applying the $P_1$ approximation for evaluating the neutron angular flux along
  the discrete ordinates $\hat{\Omega}_d$ of the $S_N$ angular quadrature set as follows:
  \begin{align}
    \Psi_{g,d} &\approx \frac{1}{4\pi}\left(\phi^\text{diff}_g+3\hat{\Omega}_d\cdot
    \vec{J}^\text{diff}_g\right) \nonumber \\
    &=\frac{1}{4\pi}\left(\phi^\text{diff}_g-3\hat{\Omega}_d\cdot D_g\nabla\phi^\text{diff}_g\right)
  \end{align}
  Therefore, the boundary source term for the $S_N$ subsolver is:
  \begin{gather}
    \Psi^\text{inc}_{g,d} = \frac{1}{w}
    \left(\phi^\text{diff}_g-3\hat{\Omega}_d\cdot D_g\nabla\phi^\text{diff}_g\right)
  \end{gather}
  where $w$ is the sum of weights of the level-symmetric quadrature set.
\end{frame}

@@

  $\vec{D}^{(i)}_g$: drift correction parameter in the $i$-th iteration
\vspace{4cm}}
  \column{.65\textwidth}
  \begin{figure}
    \centering
    \includegraphics[width=.46\textwidth]{images/algorithm}
    \begin{minipage}[b]{.49\textwidth}
      \caption{Algorithm flowchart for the hybrid $S_N$-diffusion method.}
    \end{minipage}
  \end{figure}
\end{columns}
\end{frame}

### 2024-12-05 presentation/turb-moltres.tex
slide edits

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \begin{block}{\textbf{Why the Spalart-Allmaras Model for Moltres?}}
    A computationally efficient one-equation model that provides reasonable estimates for turbulent
    effects in MSRs and is tractable for large problems on small computing clusters.
  \end{block}
  \begin{block}{\textbf{Subobjectives}}
    \textbf{Implementation of a Spalart-Allmaras turbulence model in Moltres}
    \begin{itemize}
      \item Implement a Spalart-Allmaras model in Moltres
      \item Verify and validate the model against reference turbulent flow solutions
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \textbf{Turbulent Channel Flow Verification Test Results}
  \begin{figure}[htb!]
    \centering
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{channel_vel}
      \caption{Normalized velocity distribution across the channel.}
      \label{fig:channel-vel}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{channel_nondim}
      \caption{Dimensionless velocity vs.\ dimensionless wall distance.}
      \label{fig:channel-nondim}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{channel_stress}
      \caption{Normalized stress distribution across the channel.}
      \label{fig:channel-stress}
    \end{subfigure}
    \caption{Comparison of turbulent channel flow results at Re$_\tau\approx395$ against reference
    \gls{DNS} results \cite{moser_direct_1999}. The Moltres Spalart-Allmaras model agrees consistently with
    the reference data.}
    \label{fig:channel-verification}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \textbf{Turbulent Pipe Flow Validation Test Results}
  \begin{figure}[htb]
    \centering
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{pipe_vel}
      \caption{Normalized velocity distribution across the pipe.}
      \label{fig:pipe-vel}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{pipe_nondim}
      \caption{Dimensionless velocity vs.\ dimensionless wall distance}
      \label{fig:pipe-nondim}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{pipe_stress}
      \caption{Normalized turbulent shear stress across the pipe.}
      \label{fig:pipe-stress}
    \end{subfigure}
    \caption{Comparison of turbulent pipe flow results at Re $\approx 40000$ against reference
    experimental data \cite{laufer_structure_1954}.}
    \label{fig:pipe-verification}
  \end{figure}
\end{frame}

@@

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \textbf{Backward-Facing Step Flow Validation Test Results}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}[htb!]
      \centering
      \includegraphics[width=\columnwidth]{bfs}
      \caption{Velocity magnitude distribution and streamlines around the backward-facing step. The
      streamlines illustrate the primary and secondary recirculation zones.}
      \label{fig:bfs}
    \end{figure}
    \column{5.5cm}
    \begin{table}[htb]
      \centering
      \scriptsize
      \caption{BFS flow reattachment length estimates normalized by step height $H$.}
      \begin{tabular}{l S[table-format=1.2(2)]}
        \toprule
        Source & {Reattachment length [-]} \\
        \midrule
        Experimental data & 6.26(10) \\
        CFL3D & 6.1 \\
        Moltres & 6.36 \\
        \bottomrule
      \end{tabular}
      \label{table:bfs-reattach}
    \end{table}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \textbf{Backward-Facing Step Flow Validation Test Results}
  \begin{figure}[htb]
    \centering
    \hfill
    \begin{subfigure}[b]{0.24\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{bfs_downstream_vel}
      \caption{Normalized velocity distributions downstream of step.}
      \label{fig:bfs-downstream}
    \end{subfigure} %\hfill \\
%    \centering
    \hfill
    \begin{subfigure}[b]{0.24\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{bfs_cf}
      \caption{Skin friction coefficient along the bottom wall.}
      \label{fig:bfs-cf}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.24\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{bfs_cp}
      \caption{Skin pressure coefficient along the bottom wall.}
      \label{fig:bfs-cp}
    \end{subfigure}% \hfill \\
%    \centering
    \begin{subfigure}[b]{0.24\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{bfs_stress}
      \caption{Normalized turbulent shear stress downstream
      of step.}
      \label{fig:bfs-stress}
    \end{subfigure}
    \caption{Comparison of backward facing step flow results against reference
    experimental data and computational data from CFL3D. $x/H$ values are normalized horizontal
    distances relative to the step.}
    \label{fig:bfs-plots}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \textbf{Spalart-Allmaras Model V\&V Test Summary}
  \begin{itemize}
    \item Good agreement between Moltres and reference solutions in the turbulent channel and pipe
      flow tests
    \item Good agreement between Moltres and CFL3D in the backward-facing step flow test
    \item Some discrepancy between Moltres and experimental data in the backward-facing step flow
      test, but Moltres performed better than CFL3D at predicting flow reattachment length and
      velocity/stress distributions along $x/H=1$.
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \begin{block}{\textbf{Why the Spalart-Allmaras Model for Moltres?}}
    A computationally efficient one-equation model that provides reasonable estimates for wall-bounded
    turbulent flows and is tractable for large problems on small computing clusters.
  \end{block}
  \begin{block}{\textbf{Subobjectives}}
    \textbf{Implementation of a Spalart-Allmaras turbulence model in Moltres}
    \begin{itemize}
      \item Implement a Spalart-Allmaras model in Moltres
      \item Verify and validate the model against reference turbulent flow solutions
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \textbf{Turbulent Channel Flow Verification Test Results}
  \begin{figure}[htb!]
    \centering
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{channel_vel}
      \caption{Normalized velocity distribution across the channel.}
      \label{fig:channel-vel}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{channel_nondim}
      \caption{Dimensionless velocity vs.\ dimensionless wall distance.}
      \label{fig:channel-nondim}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{channel_stress}
      \caption{Normalized stress distribution across the channel.}
      \label{fig:channel-stress}
    \end{subfigure}
    \caption{Comparison of turbulent channel flow results at Re$_\tau\approx395$ against reference
    \gls{DNS} results \cite{moser_direct_1999}.}
    \label{fig:channel-verification}
  \end{figure}
  \begin{itemize}
    \item The Moltres Spalart-Allmaras model results are consistent with reference DNS channel flow data.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \textbf{Turbulent Pipe Flow Validation Test Results}
  \begin{figure}[htb]
    \centering
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{pipe_vel}
      \caption{Normalized velocity distribution across the pipe.}
      \label{fig:pipe-vel}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{pipe_nondim}
      \caption{Dimensionless velocity vs.\ dimensionless wall distance}
      \label{fig:pipe-nondim}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{pipe_stress}
      \caption{Normalized turbulent shear stress across the pipe.}
      \label{fig:pipe-stress}
    \end{subfigure}
    \caption{Comparison of turbulent pipe flow results at Re $\approx 40000$ against reference
    experimental data \cite{laufer_structure_1954}.}
    \label{fig:pipe-verification}
  \begin{itemize}
    \item The Moltres Spalart-Allmaras model results are consistent with reference experimental pipe flow data.
  \end{itemize}
  \end{figure}
\end{frame}

@@

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \textbf{Backward-Facing Step Flow Validation Test Results}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}[htb!]
      \centering
      \includegraphics[width=\columnwidth]{bfs}
      \caption{Velocity magnitude distribution and streamlines around the backward-facing step. The
      streamlines illustrate the primary and secondary recirculation zones.}
      \label{fig:bfs}
    \end{figure}
    \column{5.5cm}
    \begin{table}[htb]
      \centering
      \scriptsize
      \caption{BFS flow reattachment length estimates normalized by step height $H$.}
      \begin{tabular}{l S[table-format=1.2(2)]}
        \toprule
        Source & {Reattachment length [-]} \\
        \midrule
        Experimental data & 6.26(10) \\
        CFL3D & 6.1 \\
        Moltres & 6.36 \\
        \bottomrule
      \end{tabular}
      \label{table:bfs-reattach}
    \end{table}
    \begin{itemize}
      \item Moltres is consistent with experimental data (within uncertainty range) while CFL3D
        falls outside the uncertainty range.
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \textbf{Backward-Facing Step Flow Validation Test Results}
  \begin{columns}
    \column{11cm}
  \begin{figure}[htb]
    \centering
    \hfill
    \begin{subfigure}[t]{0.24\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{bfs_downstream_vel}
      \caption{Normalized velocity distributions downstream of step.}
      \label{fig:bfs-downstream}
    \end{subfigure} %\hfill \\
%    \centering
    \hfill
    \begin{subfigure}[t]{0.24\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{bfs_cf}
      \caption{Skin friction coefficient along the bottom wall.}
      \label{fig:bfs-cf}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.24\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{bfs_cp}
      \caption{Skin pressure coefficient along the bottom wall.}
      \label{fig:bfs-cp}
    \end{subfigure}% \hfill \\
%    \centering
    \begin{subfigure}[t]{0.24\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{bfs_stress}
      \caption{Normalized turbulent shear stress downstream
      of step.}
      \label{fig:bfs-stress}
    \end{subfigure}
    \caption{Comparison of backward facing step flow results against reference
    experimental data and computational data from CFL3D. $x/H$ values are normalized horizontal
    distances relative to the step.}
    \label{fig:bfs-plots}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}
  \frametitle{Spalart-Allmaras Turbulence Model in Moltres}
  \begin{block}{\textbf{Spalart-Allmaras Model V\&V Test Summary}}
    \begin{itemize}
      \item Good agreement between Moltres and reference solutions in the turbulent channel and pipe
        flow tests
      \item Good agreement between Moltres and CFL3D in the backward-facing step flow test
      \item Some discrepancy between Moltres and experimental data in the backward-facing step flow
        test, but Moltres performed better than CFL3D at predicting flow reattachment length and
        velocity/stress distributions along $x/H=1$.
    \end{itemize}
  \end{block}
\end{frame}
